### 2019-12-10 Statistical Methods/03_graphical-summaries.rmd
statistical methods, ch 3
statistical methods, ch 3

```{r, echo = T}
```

@@

```{r, echo = T}
```

@@

@@

>>>>

```{r, echo = T}
n <- 50
x <- c(1, 2, 3, 4)
f <- c(0.2, 0.24, 0.4, 0.16)

stopifnot(sum(f) == 1)

xbar <- sum(x * f)
variance <- n / ( n - 1) * sum( (x - xbar)^2 * f)
stdDev <- sqrt(variance)

@@

```{r, echo = T}
n <- 10e3
x <- 0:6
f <- c(0.015625, 0.093750, 0.234375, 0.312500, 0.234375, 0.093750, 0.015625)

stopifnot(sum(f) == 1)

xbar <- sum(x * f)
variance <- ( n ) / (n - 1) * sum( (x - xbar) ^2 * f)
stdDev <- sqrt(variance)

@@

```{r, echo = T}

x <- c(5, 10, 15, 20, 25, 50)
d <- c(20, 30, 10, 40, 50, 5)
n <- sum(d)
f <- d / n

stopifnot( sum(f) == 1)

xbar <- sum(x * f)
variance <- n / (n - 1) * sum( (x - xbar)^2 * f)
stdDev <- sqrt(variance)

@@

```{r, echo = T}
x <- c(1, 5, 10, 20)
c <- c(10, 20, 40, 30)
n <- sum(c)
f <- c / n

stopifnot(sum(f) == 1)

xbar <- sum( x * f )
variance <- n / (n - 1) * sum( (x - xbar)^2 * f)
stdDev <- sqrt(variance)
